Dynein project log

### 2016-09-06 thesis_stuff/thesis_stuff.tex
Add binding constants to thesis_stuff.pdf.
Add Equipartition Theorem agreement figures to thesis_stuff.pdf.

A $\sigma = \sqrt{\frac{1}{n<W>}}$ does not make sense. For one, $\sqrt{<\Delta x>}$ should be in the numerator, since it is the
single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...\\
\\
\section{Papers}

\subsection{Winch Model (dx.doi.org/10.1016/j.bpj.2014.06.022)}
-Communication between motors and BDs possible through $\alpha$-helix sliding. Bidirectional communication. [24,25]\\
-Pre, post-powerstroke states\\
-Pre-powerstroke: unbound state after ATP hydrolysis (our onebound)\\
-Post-powerstroke: bound state (our bothbound)\\
-Elastic stalk, unlike our rigid one\\
-Only tail angle changes between pre and post-powerstroke\\
-MTBD decides directionality?\\
-Tail-tail interaction, also motor-motor stacking interaction\\
-rate constant simulation, does not do dynamics to take into account time spent in a state\\

>>>>

A $\sigma = \sqrt{\frac{1}{n<W>}}$ does not make sense. For one, $\sqrt{<\Delta x>}$ should be in the numerator, since it is the
single-timestep standard deviation. Plus it seems like for longer times the distribution would get more spread out, not less, hence
$\sqrt{n}$ should be in the numerator as well? But the CLT says it should be in the denominator...\\
\\

\section{Un/binding constants}
We let our un/binding rates $k_b$ and $k_u$ be, according to the Arrhenius equation:

\begin{align}
  k_b &= A_be^{\Delta G_{u\rightarrow b}\beta}\\
  k_u &= A_ue^{\Delta G_{b\rightarrow u}\beta}
\end{align}

Our Gibb's free energy changes are given as functions of angular state $\theta$:

\begin{align}
  \Delta G_{u\rightarrow b}(\theta) &= \sum_i \frac{1}{2}c_{bi}\Delta\theta_{bi}^2 - \sum_i \frac{1}{2}c_{ui}\Delta\theta_{ui}^2 + G_{bind}\\
  \Delta G_{u\rightarrow b}(\theta) &= \sum_i \frac{1}{2}c_{ui}\Delta\theta_{ui}^2 - \sum_i \frac{1}{2}c_{bi}\Delta\theta_{bi}^2 + G_{unbind}\\
\end{align}

\section{Equipartition Theorem}
Both bothbound and onebound states show good agreement with the equipartition theorem. Horizontal dashed line represents Equipartition Thorem energy $\frac{1}{2}k_BT$.

\begin{figure}[h!]
  \centering

  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
    \caption{Onebound PE vs time.}
  \end{minipage}
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
    \caption{Bothbound PE vs time.}
  \end{minipage}
  \label{fig:equipartition_agreement}
\end{figure}

\section{Papers}
\subsection{Winch Model (dx.doi.org/10.1016/j.bpj.2014.06.022)}
-Communication between motors and BDs possible through $\alpha$-helix sliding. Bidirectional communication. [24,25]\\
-Pre, post-powerstroke states\\
-Pre-powerstroke: unbound state after ATP hydrolysis (our onebound)\\
-Post-powerstroke: bound state (our bothbound)\\
-Elastic stalk, unlike our rigid one\\
-Only tail angle changes between pre and post-powerstroke\\
-MTBD decides directionality?\\
-Tail-tail interaction, also motor-motor stacking interaction\\
-rate constant simulation, does not do dynamics to take into account time spent in a state\\
